Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-24 paper/paper.tex
abstract.tex and intro

JavaScript (\js{}) is one of the most popular programming languages
today~\cite{redmonk-javascript,business-insider,stackify}, with
penetration in various segments including, web development, mobile,
and, more recently, the Internet of
Things~(IoT)~\cite{simply-technologies}. The interest of the community
for the language encourages constant improvements in its specification
and implementations. It is natural to expect that such improvements
lead to sensible changes in engine implementation. In fact, even small
changes can have high practical impact. For example, in October 2014 a
new attribute added to Array objects resulted in the MS Outlook
Calendar web app failing under
Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}.

>>>>

JavaScript (\js{}) is one of the most popular programming languages
today~\cite{redmonk-javascript,business-insider,stackify} with
penetration in various software development segments including, web, mobile,
and, more recently, the Internet of
Things~(IoT)~\cite{simply-technologies}. The interest of the community
for the language encourages constant improvements in its specification~\cite{ecmas262-spec}. It is natural to expect that such improvements
lead to sensible changes in engine implementations~\cite{kangax}. Even small
changes can have high practical impact. For example, in October 2014 a
new attribute added to Array objects resulted in the MS Outlook
Calendar web app failing under
Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}.
